---
title: "mpg from tidy"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
library(tidyverse)
library(plotly)

view(mpg)
?mpg
names(mpg)
class(mpg)
unique(mpg$fl)
hist(mpg$hwy)
boxplot(mpg$cty)

#wrap with drv or class
#color with manufacturer
#x = mpg$displ
#y = mpg$cty

 eng_v_cit = mpg %>% 
   ggplot(aes(x = displ,y = cty,color = manufacturer))+
   geom_point(alpha =0.4)+
   geom_smooth(method = lm, alpha = 0.2, se =FALSE, size = 0.3)+
   facet_wrap(vars(class))+
   theme_gray()+
   labs( x = "Engine displacement (litres)", 
         y = "City miles per gallon",
         title ="Engine Dislpacement vs City Miles",
         subtitle = "Seperated by type of car",
         caption = "This dataset contains a subset of the fuel economy data that the EPA makes available on https://fueleconomy.gov/. It contains only models which had a new release every year between 1999 and 2008 - this was used as a proxy for the popularity of the car.")
 
 ggplotly(eng_v_cit)
 

 
```

## Including Plots

```{r pressure, echo=FALSE}
ggplotly(eng_v_cit)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
